---
title: "ETF3231/5231 Individual Assignment 3"
author: "Changsoo Byun 31425208"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, eval=TRUE, error=TRUE, cache=TRUE)
library(fpp3)
library(readr)
library(ggplot2)
meta <- read_csv("IA_Data.csv", col_names = TRUE, n_max = 3)
# meta

# The data follows after the third row, we skip the metadata and read the data. 
# Note: Skipping the first row skips the column names, we add them back from the
#       metadata.
dat <- read_csv("IA_Data.csv", 
                # use column names from the metadata
                col_names = colnames(meta),
                # skip 4 rows as we also skip column names, specified above
                skip = 4)

# Make sure you select the column with your student ID
my_series <- dat %>% 
  # feel free to rename your series appropriately
  rename(Month = "Student ID", y ="31425208") %>%
  select(Month, y) %>% 
  mutate(Month=yearmonth(Month)) %>% 
  as_tsibble(index = Month)

train <- my_series |> 
  slice(1:441)

test <- my_series |> 
  slice(442:nrow(my_series))
```

For the tasks that follow you will be modelling the **original data without any transformations** performed (even if you previously deemed it necessary). For questions 1 to 5 use the training data, i.e., ignore the last two years of your data.

## Question 1

*Plot your time series. By observing the plot and describing its components select an ETS model you think is appropriate for forecasting. Make sure you justify your choice (no more than 150 words). (8 marks)*

```{r echo=FALSE, message=FALSE, warning=FALSE}
timeplot <- train |> 
  autoplot(y)+
  labs(title="Turnover of Supermarket and Grocery Stores",
       subtitle="New South Wales",
       y="$(millions)")

print(timeplot)
```
#Based on the time series plot of turnover in New South Wales supermarkets and grocery stores, a clear linear trend can be observed. The trend appears to be steadily increasing over time, indicating that an additive trend should be employed in the model. Multiplicative errors are useful when the data are strictly positive. Furthermore, the plot displays a multiplicative seasonality, as the seasonal pattern appears to increase proportionally with the level of the series. Therefore, a model with multiplicative seasonality will effectively capture and project the behavior of the seasonal pattern. (M, A, M)




\newpage
## Question 2

*Estimate the ETS model you described in Question 1 and show the estimated model output. Describe and comment on the estimated parameters and components. Include any plots you see necessary (no more than 150 words). (14 marks)*

```{r echo=FALSE, message=FALSE, warning=FALSE}

fit <- train |>
  model(
    mam= ETS(y ~ error("M") + trend("A") + season("M"))
  )

report(fit)

components(fit) |> autoplot()+
  labs(title ="ETS(M,A,M) components")



```
#The parameter estimates are alpha=0.2395, beta=0.0061 and gamma=0.1417. The output also returns the estimates for the intial states l[0], b[0],s[0],s[-1], s[-2], s[-3], s[-4], s[-5], s[-6], s[-7],s[-8] s[-9], s[-10] and s[-11]. The smoothing parameters is restricted to between 0 and 1, which allows the equations to be interpreted as weighted averages. The lower the AIC, AICc, and BIC values (5577.774, 5579.221, and 5647.287, respectively), the better the model fits the data.



\newpage
## Question 3

*Plot the residuals from the model and comment on these (no more than 50 words). Perform some diagnostic checks and comment on whether you are satisfied with the fit of the model. (Make sure you state all relevant information for any hypothesis test you perform such as the null hypothesis, the degrees of freedom, the decision, etc.). (10 marks)*

```{r echo=FALSE, message=FALSE, warning=FALSE}

fit %>% select(mam) %>% gg_tsresiduals()

augment(fit) |> 
  features(.resid, ljung_box,lag=24)

augment(fit) |> 
  features(.resid, box_pierce,lag=24)

```
#The null hypothesis is the spike is 0 assuming the residuals are white noise. Computed in 95% CI and 24 degrees of freedom as it is seasonal. The results of the tests are statistically significant, having enough evidence to reject the null hypothesis. Hence, residuals are not white noise.



\newpage
## Question 4

*Let R select an ETS model. What model has been chosen and how has this model been chosen? (No more than 100 words). (6 marks)*

```{r}
fit2 <- train |>
  model(auto=ETS(y))
report(fit2)
```
#Model selection is using information criteria such as the AIC, AICc, and BIC. These criteria balance the trade-off between goodness-of-fit and model complexity. A lower value of these criteria suggests a better model. To illustrate this, several models, such as ETS(A,A,M), ETS(M,M,M), ETS(A,A,A), and ETS(M,A,A), could be compared to determine which one is the best fit for the data.


\newpage
## Question 5

*Comment on how the model chosen by R is different to the model you have specified (no more than 50 words). Which of the two models would you choose and why? (no more than 50 words). (Hint: think about model selection here but also check your residuals).* 

*If the models are identical specify a plausible alternative. Give a brief justification for your choice (no more than 100 words). (Hint: also check the residuals from this model).  (12 marks)*

```{r}
fit2 <- train |>
  model(
    ETS_auto = ETS(y),
    ETS_AAA = ETS(y ~ error("A") + trend("A") + season("A")),
    ETS_damped = ETS(y ~ error("A") + trend("Ad")),
    ETS_forbidden = ETS(y ~ error("A") + trend("Ad") + season("M"))
  )


glance(fit2)
```
#I got the identical ETS model/ Among the evaluated ETS models, ETS(M,A,M) which is auto exhibits the lowest AIC score, indicating it is the most appropriate choice as the ETS model. However, ETS_forbidden shows the best fit among the other models based on MSE and has the second lowest AIC and AICc scores, which are the preferred criteria for selecting the best ETS model. Therefore, ETS(A,Ad,M) could be a plausible alternative ETS model to consider.

\newpage
## Question 6

*Generate forecasts for the last two years of your sample using both alternative ETS models (you will need to re-estimate both models over the appropriate training sample). Plot the forecasts and forecast intervals. Briefly comment on these. Which model does best? (No more than 100 words). (8 marks)*

```{r}
fc <- fit |> 
  forecast(h="2 years")

fc |> 
  autoplot(
    my_series
    )+
  labs(y= "$(millions)",
       title= "Forecasts for montly turnover of supermarket and grocery stores")

fit3 <- train |>
  model(
     ETS_forbidden = ETS(y ~ error("A") + trend("Ad") + season("M"))
     )

fc2 <-  fit3 |> 
  forecast(h="2 years")

fc2 |> 
  autoplot(
    my_series
    )+
  labs(y= "$(millions)",
       title= "Forecasts for montly turnover of supermarket and grocery stores")
  
  

```

#Both plots display the point forecasts and 80% and 95% prediction intervals for the turnover of supermarket and grocery stores in New South Wales, using two different models: ETS(M,A,M) and ETS(A,Ad,M). The point forecasts for both models appear reasonable, and the intervals are relatively narrow. However, upon closer inspection, the first plot, which represents the ETS(M,A,M) model, closely aligns with the original sample plot, suggesting that this model may provide more accurate forecasts than the ETS(A,Ad,M) model.

\newpage
## Question 7

*Generate forecasts for the two years following the end of your sample using your chosen model. Plot them and briefly comment on these. (No more than 100 words).  (4 marks)*

```{r}
my_series |> 
  model(ETS(y ~ error("M") + trend("A") + season("M"))) |> 
  forecast(h="2 years") |> 
  autoplot(my_series)

```
#The plot displays the predicted turnover for supermarket and grocery stores in New South Wales using an ETS(M,A,M) model, including 80% and 95% prediction intervals. The model's point forecasts appear reasonable, and the narrow intervals indicate that the model performs well in capturing the trends and seasonal patterns in the data. Furthermore, the ETS(M,A,M) model produces the minimum AIC, which suggests that it is the best model to use for accurate predictions.
